asc_file_database

### 2019-03-11 src/stack_test.Rmd
stack loop prediction complete. model fiddling now

>>>>

```{r}
# now loop to create stacks
janpres <- read.csv("../output/bio/maxenttestjanpr.csv", header = TRUE)
janpres$occ <- 1
janab <- read.csv("../output/bio/maxenttestjanab.csv", header = TRUE)
janab$occ <- 0
prab <- rbind(janpres, janab)
prab$originalscientificname <- "cap" #because species name needs to be the same
pa <- prab$occ
prab <- subset(prab, select = -c(x, y, occ, originalscientificname)) #ok so for maxent in r just need the variables
prab

system.file("java", package="dismo") #finding location to put maxent jar file
system("java -version")
mod1 <- maxent(x = prab, p = pa, path = paste0("../output/maxentout"), args =  c("responsecurves"), save(md, file = "../output/maxentmod"))

for (td in 1:nrow(unlayer)){
  temp_depth <- raster(unlayer$temp_depth[td])
  crs(temp_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(temp_depth) <- "temp_depth"
  temp_depth <- projectRaster(temp_depth, aea)
  chl_surface <- raster(unlayer$chl_surface[td])
  crs(chl_surface) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(chl_surface) <- "chl_surface"
  chl_surface <- projectRaster(chl_surface, aea)
  o2_depth <- raster(unlayer$o2_depth[td])
  crs(o2_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(o2_depth) <- "o2_depth"
  o2_depth <- projectRaster(o2_depth, aea)
  salinity_depth <- raster(unlayer$salinity_depth[td])
  crs(salinity_depth) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(salinity_depth) <- "salinity_depth"
  salinity_depth <- projectRaster(salinity_depth, aea)
  nao_sample <- raster(unlayer$nao_sample[td])
  crs(nao_sample) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" 
  names(nao_sample) <- "nao_sample"
  nao_sample <- projectRaster(nao_sample, aea)
  nao_winter <- raster(unlayer$nao_winter[td])
  crs(nao_winter) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
  names(nao_winter) <- "nao_winter"
  nao_winter <- projectRaster(nao_winter, aea)
  stackn <- unlayer$stackname[td]
  test <- stack(temp_depth, chl_surface, o2_depth, salinity_depth, nao_sample, nao_winter)
  #stackSave(test,unlayer$stackname[td])
  pred <- predict(mod1, test, file = paste0("../output/maxentpredict/", stackn), overwrite=TRUE) 
  paste("maxplot_", stackn, ".png", sep = "") # to automatically save the plot to a png AND show it inline
  preplot <- plot(pred, png(paste0("../output/maxentpredict/", stackn, ".png")))
  dev.off() # stops automatic saving of the plot to a png
}
